\cvsection{Work Experience}

\begin{cventries}

\cventry
{Sustainability Consultant}
{\href{https://syntexgreen.tech}{Syntex GreenTech}}
{Perugia, Italy}
{Oct. 2023 - Present}
{\begin{cvitems}
\item {Development of ESG strategy based on innovation.}
\item {Support ESG financing decisions and reduction of financial risk.}
\item {Sustainability reporting.}
\item {Analysis of impacts, risks and opportunities in relation to sustainability issues.}
\end{cvitems}}

\cventry
{Research and Teaching assistant}
{\href{https://unibz.it}{Free University of Bozen-Bolzano}}
{Bozen, Italy}
{Nov. 2022 - Present}
{\begin{cvitems}
\item {Development and implementation of experimental setups.}
\item {Design and execution of laboratory experiments, collection and analysis of data.}
\item {Contribution to the preparation of research papers, conference abstracts, grant proposals, and project reports.}
\item {Support in teaching activities by mentoring students, and giving exercise classes.}
\item {Contribution to the supervision of PhD students.}
\end{cvitems}}

\cventry
{ISO 27001:2013/2022 Auditor trainee}
{Freelancer}
{Italy}
{Aug. 2021 - Present}
{\begin{cvitems}
\item {As an ISO 27001 Auditor Trainee, I have undergone lead auditor training in ISO/IEC 27001:2013 and ISO/IEC 27001:2022, focusing on Information Security Management. My role involves gaining practical experience and skills in auditing and assessing information security management systems.}
\end{cvitems}}

\cventry
{Visiting PhD Candidate}
{\href{https://www.en.aau.dk/}{Aalborg University}}
{Aalborg, Denmark}
{May. 2022 - Sep. 2022}
{\begin{cvitems}
\item {Supercritical water upgrading of distillation residues of hydrotreated HTL-crude oil; HTL-crude oil upgrading.}
\end{cvitems}}

\cventry
{PhD Candidate}
{\href{https://unibz.it}{Free University of Bozen-Bolzano}}
{Bozen, Italy}
{Oct. 2019 - Oct. 2022}
{\begin{cvitems}
\item {Development and implementation of experimental setups.}
\item {Design and execution of laboratory experiments, collection and analysis of data.}
\item {Contribution to the preparation of research papers, conference abstracts, grant proposals, and project reports.}
\end{cvitems}}

\cventry
{Consultant}
{Freelancer}
{Italy}
{Oct. 2018 - Oct. 2019}
{\begin{cvitems}
\item {Dealer training for stock audit on assignment from a certifying organization for a leading heavy machinery manufacturer.}
\end{cvitems}}

\cventry
{Consultant and Auditor}
{Freelancer}
{Italy}
{Jul. 2018 - Present}
{\begin{cvitems}
\item {ISO/IEC 27001 - Information Security Management internal audits for a consulting company.}
\end{cvitems}}

\cventry
{Auditor}
{Freelancer}
{Europe}
{Apr. 2017 - Oct. 2019}
{\begin{cvitems}
\item {2nd party compound audit on assignment from a certifying organization for a leading automobile manufacturer.}
\item {Audits held in Italy and abroad (Austria, Germany, Finland, Poland, Portugal, Sweden).}
\end{cvitems}}

\cventry
{Consultant}
{Freelancer}
{Perugia, Italy}
{Oct. 2016 - Oct. 2019}
{\begin{cvitems}
\item {CE homologation processes of motorcycle helmets, goggles and gloves.}
\item {Management of relationships with suppliers, mainly not Italian (China and Pakistan).}
\end{cvitems}}

\end{cventries}