%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Education}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

  %---------------------------------------------------------
  \cventry
  {PhD in Sustainable Energy and Technologies} % Degree
  {Free University of Bozen-Bolzano} % Institution
  {Bozen, Italy} % Location
  {Oct. 2019 - Oct. 2022} % Date(s)
  {
    \begin{cvitems} % Description(s) bullet points
      \item {Thesis: Hydrothermal liquefaction of biomass and biocrude upgrading: fundamentals, experimental analysis and modelling.}
      \item {Spent 5 months as a visiting PhD in the Advanced Biofuels Lab of Aalborg University, Denmark.}
      \item {Developed and commissioned a pilot plant for the production of biocrude oil to be upgraded to SAF (Sustainable Aviation Fuels).}
      \item {Process modelling through optimization algorithms to find thermodynamic equilibrium.}
      \item {Performed techno-economic analysis to optimize process conditions and reduce costs.}
      \item {Support in the supervision of master students.}
      \item {Preparation of technical reports, visualizations, and presentations.}
    \end{cvitems}
  }

  %---------------------------------------------------------
  \cventry
  {M.Sc. in Energy Engineering} % Degree
  {Free University of Bozen-Bolzano} % Institution
  {Bozen, Italy} % Location
  {Sep. 2017 - Oct. 2019} % Date(s)
  {
    \begin{cvitems} % Description(s) bullet points
      \item {Thesis: Valorization of residues from parapharmaceutical and herbal medicine production: a case study.}
      \item {Performed techno-economic analysis to optimize process conditions of a parapharmaceutical company.}
    \end{cvitems}
  }

  %---------------------------------------------------------
  \cventry
  {B.E. in Mechanical Engineering} % Degree
  {University of Perugia} % Institution
  {Perugia, Italy} % Location
  {Sep. 2013 - Apr. 2017} % Date(s)
  {
    \begin{cvitems} % Description(s) bullet points
      \item {Erasmus + of 6 months at the FAU Erlangen-Nürnberg, Germany.}
    \end{cvitems}
  }

  %---------------------------------------------------------
\end{cventries}
