%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

  %---------------------------------------------------------
  \cventry
  {Sustainability Consultant} % Job title
  {\href{https://syntegreen.tech}{Syntex GreenTech}} % Organization
  {Perugia, Italy} % Location
  {Oct. 2023 - Present} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Developed an innovative ESG strategy, driving sustainability while reducing financial risks through data-backed decision-making.}
      \item {Conducted comprehensive sustainability impact assessments, identifying key risks and opportunities for business growth.}
      \item {Developed Sustainability reports following both the GRI and EFRAG frameworks.}
      \item {Developed autonomously a platform to speed up the collection of information and monitoring of KPIs.}
    \end{cvitems}
  }

  %---------------------------------------------------------
  \cventry
  {Postdoctoral Research and Teaching assistant} % Job title
  {\href{https://unibz.it}{Free University of Bozen-Bolzano}} % Organization
  {Bozen, Italy} % Location
  {Nov. 2022 - Present} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {FRONTSH1P project - A FRONTrunner approach for the transition to a circular and resilient future: deployment of systemic solutions with the support of local clusters and the development of regional community-based innovation schemes.}
      \item {Performed techno-economic analysis to optimize process conditions and reduce costs.}
      \item {Developed simulations and models to foster the understanding of thermochemical processes.}
      \item {Applied data analysis techniques to experimental datasets, such as peak de-convolution and curve fittings.}
      \item {Developed a machine learning model to predict the biocrude oil yield.}
      \item {Teaching assistant for the course Energetics of the B.Sc. in Industrial and Mechanical Engineering, and M.Sc. in Energy Engineering.}
      \item {Support in the supervision of PhD and Master students.}
    \end{cvitems}
  }

  %---------------------------------------------------------
  \cventry
  {ISO 27001 Auditor trainee} % Job title
  {\href{https://sgs.com}{SGS}} % Organization
  {Italy} % Location
  {Aug. 2021 - Present} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {ISO/IEC 27001:2013 - Information Security Management lead auditor training.}
      \item {ISO/IEC 27001:2022 - Information security, cybersecurity and privacy protection.}
    \end{cvitems}
  }

  %---------------------------------------------------------
  \cventry
  {Consultant} % Job title
  {\href{https://sgs.com}{SGS}} % Organization
  {Italy} % Location
  {Oct. 2018 - Oct. 2019} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Dealer training for stock audit on assignment from a certifying organization for a leading heavy machinery manufacturer.}
      \item {Audits held in Italy.}
    \end{cvitems}
  }

  %---------------------------------------------------------
  \cventry
  {Consultant and Auditor} % Job title
  {\href{https://www.qualitas.eu}{Qualitas S.r.l.}} % Organization
  {Perugia, Italy} % Location
  {Jul. 2018 - Present} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {ISO/IEC 27001:2013/2022 - Information Security Management internal audits for a consulting company.}
      \item {Provided strategic recommendations to improve data protection protocols and ensure regulatory compliance.}
    \end{cvitems}
  }

  %---------------------------------------------------------
  \cventry
  {Auditor} % Job title
  {\href{https://sgs.com}{SGS}} % Organization
  {Europe} % Location
  {Apr. 2017 - Oct. 2019} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {2$^{nd}$ party compound audit on assignment from a certifying organization for a leading automobile manufacturer.}
      \item {Audits held in Italy and abroad (Austria, Germany, Finland, Poland, Portugal, Sweden).}
    \end{cvitems}
  }

  %---------------------------------------------------------
  \cventry
  {Consultant} % Job title
  {\href{https://www.baruffaldi.net/}{Baruffaldi S.r.l.}} % Organization
  {Perugia, Italy} % Location
  {Oct. 2016 - Oct. 2019} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {CE homologation processes of motorcycle helmets, goggles and gloves.}
      \item {Management of relationships with suppliers, mainly not Italian (China and Pakistan).}
    \end{cvitems}
  }
  %---------------------------------------------------------
\end{cventries}
